\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[greek,english]{babel}
\usepackage{alphabeta} 
\usepackage[pdftex]{graphicx}
\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
\linespread{1.06}
\setlength{\parskip}{8pt plus2pt minus2pt}
\widowpenalty 10000
\clubpenalty 10000
\newcommand{\eat}[1]{}
\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
\usepackage[official]{eurosym}
\usepackage{enumitem}
\setlist{nolistsep,noitemsep}
\usepackage[hidelinks]{hyperref}
\usepackage{cite}
\usepackage{lipsum}
\begin{document}

\begin{center}
    \HRule \\[0.4cm]
    {\LARGE
    \textbf{ECE 351 Lab 0 Deliverables}
    \HRule \\[0.4 cm]}
    {\large 
    Jonathan Stark \\[0.4cm]
    January 24, 2023}
\end{center}
\section{Questions}
\begin{enumerate}
    \item What are you planning to do this upcoming Summer?\\[0.1cm]
    I plan to hopefully get an internship. I don't know with which company I would do this with but hopefully it will be in either the Boise or Moscow area. I would also be willing to participate in an internship in Southern California or Florida as I have family in these states. Speaking of family I hope to visit my brother and his family. He and his wife have four children ages 6, 8, 10, and 12. Additionally, last September, I participated in a sprint triathlon and did well enough to be invited to the US sprint triathlon nationals which would be happening at the start of August of this year in Wisconsin. \\[0.2cm]
    
    \item What do you personally want to get out of this lab?\\[0.1cm]
    Coming out of this lab, I hope to have a proficient understanding of python that I will be able to encounter most basic problems that may require coding and not feel unencumbered by these challenges. Additionally, within this class, I hope to practice problem solving methods, especially as that is the main tool that engineers use throughout their professional careers. I am excited to learn more about python and LaTeX since these tools are profusely used throughout industry. I have been told that once learning a coding language that learning others becomes quite easier as well.
    
\end{enumerate}



\bibliographystyle{ieeetr}
\bibliography{refs}
\end{document}